One Amazon Problem? Problem-constructions and Transnationalism in Brazilian Presidential Discourse since 1985

### 2023-02-16 Submission/Re-submission/draft/draft_resubmission_shorten.rmd
Removed space in footnotes in text to improve word count

We use a support-vector machine algorithm, a non-probabilistic linear classifier appropriate for binary categories [@meyer2021; @noble2006], to train a model to label text. The model was validated by testing it on the validation set. As a robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would. The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements [^1]. Automating the code saved the authors about two months.

@@

Looking at speeches that mention the Amazon over time (model 1) reviews several interesting trends. Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year. By investigating its development in time, we can identify instances when the Amazon in itself becomes more urgent as a problem, and when not. On average, presidents mention the Amazon in 15.5% of their speeches [^3]. This suggests the Amazon is a topic of relative high importance for presidents generally. However, we observe four peak years (one standard deviation from the mean) in the figure: 1989, 1992, 2009, and 2019. We find that these peak years coincide with high-profile environmental events, but not with domestic policy adoption.

@@

While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends. Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985. Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3 [^4].

>>>>

We use a support-vector machine algorithm, a non-probabilistic linear classifier appropriate for binary categories [@meyer2021; @noble2006], to train a model to label text. The model was validated by testing it on the validation set. As a robustness check, the authors randomly select 100 automatically coded statements and find that the automated model is 95% accurate in coding these statements as the authors would. The final dataset, excluding false positive matches, contains 1924 coded Amazonian statements[^1]. Automating the code saved the authors about two months.

@@

Looking at speeches that mention the Amazon over time (model 1) reviews several interesting trends. Figure 2, below, shows the proportion of speeches that mentions the Amazon in relation to all speeches in a year. By investigating its development in time, we can identify instances when the Amazon in itself becomes more urgent as a problem, and when not. On average, presidents mention the Amazon in 15.5% of their speeches[^3]. This suggests the Amazon is a topic of relative high importance for presidents generally. However, we observe four peak years (one standard deviation from the mean) in the figure: 1989, 1992, 2009, and 2019. We find that these peak years coincide with high-profile environmental events, but not with domestic policy adoption.

@@

While we identified the effects of setting and urgency on problem-constructions (models 2-5), the developments of problem-constructions in time also reveal unique trends. Figure 3, below, illustrates the annual share of pure-types problem-constructions since 1985. Interestingly, peak years identified in Figure 2 (above) do not coincide with increases of specific problem-constructions in Figure 3[^4].
